\setstretch{1.3} % Reset the line-spacing to 1.3 for body text (if it has changed)

\acknowledgements{\addtocontents{toc}{\vspace{1em}} % Add a gap in the Contents, for aesthetics
%\epigraph{Not enough people in this world, I think, carry a cosmic perspective with them. It could be life-changing.}{Neil deGrasse Tyson}
%\epigraph{TheBigBangTheory: When geeky scientists can be main characters in a hit primetime series, you know there's hope for the world.}{Neil deGrasse Tyson}

%\epigraph{Not enough people do things that leave others to wonder.  RT @BrianMendicino: Wondering why @neiltyson is watching Glee.}{Neil %deGrasse Tyson}

%\epigraph{In whatever you choose to do. Do it because it's hard, not because it's easy.}

\epigraph{Look up at the stars and not down at your feet. Try to make sense of
what you see, and wonder about what makes the universe exist. Be curious.}
{Stephen Hawking}

Phew, I feel so relief to fulfill this thesis without a sip of red bull or
other beverages at all (except for coffee). This is a significant
accomplishment in my life and it would be impossible without all the people
who supported and believed in me.

I like to give my sincere thanks and extend my gratitude to my honorable
supervisor Prof. Juan Carlos Niebles. I sincelery thank him for an exemplary
guidance and encouragement. His endless support inspired me to make
the right decisions in the most important moments and I am glad to work under
his supervision. 

I would like to thank my friends and specially to all VisionLab members for
all the thoughtful and mind stimulating conversations we had, which helped me
to think wisely and outside the box. I've enjoyed the companionship that you
all have brought to me, during these year. 

Last, but not least, I would like to thank my parents, who taught me the value
of hard work using themselves as an example. Giving me enormous support during
my whole life, they steered me into the right path and served me as a guidance.
I feel very thankful for having them as parents.

}
