% Chapter Template

\chapter{Introduction} % Main chapter title

% For referencing this chapter elsewhere, use \ref{ChapterX}
\label{chapter::introduction} 

\lhead{Chapter 1. \emph{Introduction}} 

\textbf{Keywords: }Computer vision, object tracking, object model, spatial
clustering, inliers, outliers, ensemble.

The goal of visual object tracking is to estimate the state of a target in an
image sequence.
This is a difficult task, as the target object can be articulated or
deformable, the scene illumination can change suddenly, background
clutter may introduce distractions that result in tracker drifting,
among others. In spite of the multiple challenges, there are many potential
applications that make this capability attractive such as
activity recognition, motion analysis, human surveillance and robotics.

%In order to cope with some of these challenges, many approaches for
%object tracking have been proposed, each attempting to solve one or several
%of such issues.
Many approaches for object tracking have been proposed to cope with some of
these challenges.
%While current methods can achieve relative success,
While the state-of-the-art methods achieve relative success,
there is still no single approach that is able to handle all challenging
situations.
%For instance, tracking-by-detection methods generally have the problem of
%not handling scale variations correctly.
For instance, tracking-by-detection methods may not be able to handle scale
variations rigorously.
%On the other hand, simpler methods tend to suffer from model drifting and
%struggle to handle strong illumination changes.
On the other hand, generative methods tend to suffer from model drifting and
struggle to handle appearance variations.

In this thesis, we focus on ``model free tracking'' of
arbitrary objects in videos, in which no prior knowledge other than
the object location in the first frame is available.
Recently, the online tracking benchmark proposed in \cite{Wu2013B}
shows that
each tracking algorithm performs best under particular circumstances.
There is no single tracking algorithm that can perform well on all
sequences in the benchmark. This indicates that each tracking challenge
can be addressed better by a different algorithm. In other words,
tracking strenghts may be distributed among the available trackers.
This is the key observation that inspires our proposed method;
we consider a tracking approach that combines the outputs
of multiple trackers running in parallel via an online ensemble.
This ensemble has the interesting property of leveraging the strenghts
of individual trackers, while overcoming the failure modes of
each  tracker. Since for a new and unseen sequence we do
not know which tracker would perform best, our method computes
a data-driven online ensemble that results in improved tracking performance
when compared to the results of individual trackers.

\iffalse
Taking this into account, we consider an approach that combining the
virtues of different algorithms, while evading their weaknesses, could
outperform each single algorithm. Just as "two heads are better than one",
making trackers perform this task together in an unknown scenario, may
result in a higher level of performance and achievement, than could be
obtained individually. This is what in psychology states as "positive
interdependence", the ability of group members to encourage and
facilitate each other's efforts \cite{Johnson1998}.
\fi

%In our method, we leverage the fact that for a given sequence, only
%some of the trackers fail and they do so drifting into different
%parts of the image, while some of the trackers succeed by focusing on
%the correct target.
In our method, we leverage the observation that only some of the trackers
drift into non-target areas of the image in most cases while some of the
trackers succeed by focusing on the correct target.
Furthermore, our ensemble uses an appearance model
that serves as an additional verification mechanism of the tracked region.
%{\color{blue}[This sentence is weird. Appearance model verifies appearance?]}
%We are motivated to link trackers
%together so one cannot succeed, unless all group members succeed.
%A common tracking system consists of an appearance model, which can
%evaluate the likelihood of the object of interest at a given location.
%A motion model, that stores and contains the locations of the object
%over time. Finally, a search strategy to find the best location in the
%current frame \cite{Yilmaz2006}.
%All tracking approaches share the same
%goal, meaning that each tracker's individual "effort" is required and is
%indispensable for group success.
Using these model components, we identify and exploit the successful trackers
to steer failed trackers towards the correct target region. Effectively,
our ensemble can correct failed trackers, which ultimately increases
tracking performance.

\section{Goals} \label{sec::goals}

\textbf{Our main goal} is to design and implement a visual object tracking
system, performing an ensemble of multiple tracking algorithms (trackers). We
aim at selecting a set of standarized sequences, to be used for analysis, development and tests of the proposed system. We need to select a group of
trackers, which can store its state on each frame and be possible its
reinitialization. We seek to develop an ensemble of multiple trackers
algorithms. We plan to test and verify our approach behavior using performance
quantification.

\section{Contributions}

The main contribution of this thesis is an ensemble tracking
framework that builds on top of the output of available online tracking
algorithms running in parallel to produce an online fused tracking result that
leverages each tracker best features. Our method does not use prior knowledge
about the nature of the trackers in the pool.
The fused tracking output is obtained by considering appearance and spatial
relations among tracker outputs.
In order to cope with trackers weaknesses,
our ensemble identifies successful trackers in a data-driven fashion
and uses them to steer failed trackers by restarting them asynchronously.
This helps to avoid sequence dependent parameters and overtuning.

\section{Thesis overview}

The remainder of this thesis is organized as follows.
We first briefly review the state-of-the-art of tracking algorithms
in Chapter \ref{chapter::related_work} and
then present our online ensemble tracking algorithm
in Chapter \ref{chapter::approach}.
Chapter \ref{chapter::experiments} illustrates quantitative and qualitative results of our
tracker on a standard benchmarking dataset.
%we present quantitative and qualitative results of our
%tracker on a standard benchmarking dataset in
%Chapter \ref{sec:experiments}.
Finally, we conclude the thesis in Chapter \ref{chapter::conclusions}.